\pagestyle{empty}
\section{Survey Results\\{\small\tt{R.~Hales}}}

As poster fair involved showing a number of people a stable release of our project, we decided it would be a good chance to have users test our project and to see how well they felt it met our aims. To do this testing we created a short survey for the users to fill in after using the simulation.  In total we had twelve people answer our survey.

\subsection{How realistic is our simulation?}

Since our goal was to create a realistic simulation of zombies, the first question we asked was how realistic is our simulation? This was to be answered with a number between 1 and 5, 1 being not very realistic and 5 being very realistic. We had an average result of 4.3 with no users answering below 4. Therefore every user we surveyed thought our simulation was realistic.

\subsection{How easy to understand is our system?}

We also wanted to know how much users could understand about the behaviour of the system without having to have it explained in great detail. Again we asked for answers between 1 and 5, with 1 being very difficult to understand and 5 being very easy to understand. We had an average result of 4.3, with a range of 3 to 5 given as answers. Thus showing our system was largely understood at least fairly easily.

\subsection{How easy to understand is the user interface?}

As well as the actual system, we also wanted to know specifically how easy to understand our user interface was. Again answers were given between 1 and 5, with 1 being very difficult to understand and 5 being very easy to understand. We had an average result of 4.2, with a range of 2 to 5 given as answers. This showed the user interface was largely understood but there is room for improvement as some people had trouble with it.Based on feedback changing the sprites to more clearly respresent zombies and humans and making it more obvious that entities are clickable are the most obvious improvements.

\subsection{Is our simulation speed too fast or slow?}

One subject we were concerned with was the speed of our simulation, if it is too fast it can become hard to follow and understand, whereas if it is too slow it can become uninteresting and hard to see behaviour clearly. For the survey we asked the users to answer whether they thought  the simulation was much too slow, slightly too slow, the correct speed, slightly too fast or much too fast to help us decide on a speed for the simulation. Two thirds of people said the speed was fine as it was, everyone who did not said the speed was too slow although only one person thought it was much too slow. As such we decided to keep the speed the same.


\subsection{Are there any changes you would make to our simulations behaviour?} 

We asked our users if they'd make any changes to the simulations behaviour, in case there were suggestions we would not have considered otherwise. We got the same suggestion multiple times, humans should be able to fight back against zombies and have a win case.  This was a feature we had hoped to include since early in development but did not have time for ultimately.

\subsection{Are there any changes you would make to the user interface?}

We also asked users if they would make changes to the user interface for the same reasons we asked about changing simulation behaviour. The most common answer was to make the interface more visually appealing, with some people suggesting the visuals should match with the concept more.
We also got several suggestions to make the animation of the simulation smoother. As well as these one person asked to make the entities easier to select while the simulation is running and another asked to make it easier to tell selected entities apart.

\subsection{Do you have any other comments you would like to make about our system?}

Although we asked this question, none of our users had any extra suggestions to make.

\clearpage
\endinput
