\pagestyle{empty}

\section{Types of Zombie\\{\small\tt{J.~Pearse}}}
The background material on Zombies is broadly split into two types of explanations for the existence of zombie humans;
\begin{description}
\item[Supernatural] phenomenon are responsible for reanimating human corpses.\footnote{White Zombie (1932), The Evil Dead (1981)} These animated corpse zombies are created with black magic and respond to the wishes of their creator. This type of Zombie is therefore not acting entirely independently and of little use in our simulation. Similarly the Zombie of Haitian Voodoo mythology, although not actually dead are enslaved to a Houngan sorcerer.
\item[Biological] albeit fantastic explanations, where the existence of zombies is the result of some type of virus or parasite, details vary from fiction to fiction but by picking and choosing between these ideas we can construct a Zombie conceit which is at the very least logically coherent.
\end{description}
\subsection{Observations}
\begin{itemize}
\item Zombies may be able to react differently to injury than non infected humans, ignoring pain. But a fatal wound, massive blood loss or damage to vital organs will eventually the kill the host.
\item
Zombies are attracted by sound and movement but are somehow deterred from biting already symptomatic individuals, in many accounts the Zombies use scent to search out prey.
\end{itemize}

\subsection{Conclusion}
The hypothesis of our simulation is that the attraction to movement and sound is what causes the Zombies to group together in hordes and this is what our simulation is designed to explore. The path-finding abilities of the zombies are very limited.
Since zombies are not noted for their self-preservation instincts their motivations can be broken down as;
\begin{enumerate}
\item I can bite someone $\rightarrow$ Bite them.
\item I can detect someone to bite $\rightarrow$ Move towards them.
\item I can detect a suggestion of someone to bite $\rightarrow$ Move towards the stimulus.
\end{enumerate}
\clearpage
\endinput
